---
title: "Homework 3"
output: pdf_document
---




```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```
```{r data import}
raw_stx <- read.delim("game_data_public.STX.Sealed.csv",header = TRUE,sep = ",")
```
```{r turns column}
turns <- select(raw_stx,"num_turns")
```


## 17lands.com Strixhaven Game Data

Strixhaven the most recent expansion for the Magic the Gathering trading card game.  17lands provides a service where online Magic the Gathering players can track their gameplay and in return provide them with aggregated gameplay data.  The data set consists of `r ncol(raw_stx)` variables for each of the `r nrow(raw_stx)` games recorded in the dataset.  One interesting variable is the number of turns a game of Strixhaven takes.  The mean number of turns a game takes is `r sapply(turns, mean, na.rm=TRUE)` with a standard deviation of `r sapply(turns, sd, na.rm=TRUE)`.  The minimum number of turns recorded is `r sapply(turns, min, na.rm=TRUE)` and the maximum number of turns is `r sapply(turns, max, na.rm=TRUE)`.  Below is a bar chart of the turn data for Strixhaven. 

```{r turn plot}
ggplot(raw_stx,aes(num_turns)) + geom_histogram()
```
```{r Color Percentages}
color <- raw_stx %>% 
  count(opp_colors) %>% 
  arrange(desc(n)) %>% 
  mutate(m=n/nrow(raw_stx)*100)
  
```

In addition we have access to deck color data.  In Magic the Gathering there are 5 colors of resources available to players, and players can choose any combination of these 5 colors which in many ways define what and how their decks will play.  The variable "opp_colors" is the color identity that an opponent's deck was, with each color having a letter code.  So for example a code of "WUR" means the deck was white, blue and red.  There are `r color[26,2]` or `r color[26,3]`% na's.  The percent makeup of decks for each color range from `r color[1,3]`% to `r color[32,3]`%.  Below we can see a bar chart of how many decks there are for each color combination.
```{r color plot}
ggplot(color,aes(x=opp_colors,y=n)) + geom_bar(stat='identity')
```

This plot shows that there are really ten major color combinations that are represented while the other 21 do not make up much of the makeup.  So a better graph would look like this.

```{r top ten color plot}
color %>% 
  slice(1:10) %>% 
  ggplot(aes(x=opp_colors,y=m)) + geom_bar(stat='identity')
```